% SPDX-FileCopyrightText: 2025 IObundle
%
% SPDX-License-Identifier: MIT

%
% Main classes
%

The Py2HWSW tool uses the \href{https://github.com/IObundle/py2hwsw/blob/main/py2hwsw/scripts/if_gen.py}{if\_gen.py} script to generate the signals of standard interfaces.

The list of standard interfaces currenlty supported by the if\_gen.py script are listed below.

% py2_macro: listing mem_if_details from if_gen.py
% py2_macro: listing if_details from if_gen.py

When a user specifies a standard interface for a port~\ref{sec:iob_port} or a wire~\ref{sec:iob_wire}, a new instance of the `interface` class is created to represent it.

% py2_macro: class_attributes interface from if_gen.py

This class stores the interface properties which will then be used by interface specific functions to generate the signals.
Each attribute of the interface class is preceded by a comment describing the purpose of the attribute.

Each interface supported by if\_gen.py contains its own `get\_\textless interface\textgreater\_ports` function, and returns a list of signals for the interface.

%
% AXI Stream
%
\clearpage
\large\textbf{AXI Stream}

The AXI Stream interface uses the `get\_axis\_ports` function of the \href{https://github.com/IObundle/py2hwsw/blob/main/py2hwsw/scripts/if_gen.py}{if\_gen.py} script.

% py2_macro: listing get_axis_ports from if_gen.py

It has the configurable width: DATA\_W

For example, to add an AXI Stream port to a core, add the following python dictionary to the core's ports list:
\begin{lstlisting}[language=python]
{
	"name": "example_port_m",
	"descr": "AXI Stream manager port",
	"signals": {
		"type": "axis",
		"DATA_W": 32,
	},
},
\end{lstlisting}


%
% AXI Lite
%
\clearpage
\large\textbf{AXI Lite}

The AXI Lite interface uses the `get\_axil\_ports` function of the \href{https://github.com/IObundle/py2hwsw/blob/main/py2hwsw/scripts/if_gen.py}{if\_gen.py} script.

% py2_macro: listing get_axil_ports from if_gen.py
% py2_macro: listing get_axil_read_ports from if_gen.py
% py2_macro: listing get_axil_write_ports from if_gen.py

It has the configurable widths: 
\begin{itemize}
  \item ADDR\_W
  \item DATA\_W
  \item PROT\_W
  \item RESP\_W
\end{itemize}

The AXI Lite interface also supports the the following 'params':
\begin{itemize}
  \item prot: Include "prot" signal
\end{itemize}

For example, to add an AXI Lite port to a core, add the following python dictionary to the core's ports list:
\begin{lstlisting}[language=python]
{
	"name": "example_port_m",
	"descr": "AXI Lite manager port",
	"signals": {
		"type": "axil",
		"ADDR_W": 32,
		"DATA_W": 32,
		"PROT_W": 3,
		"RESP_W": 2,
	},
},
\end{lstlisting}


%
% AXI
%
\clearpage
\large\textbf{AXI}

The AXI interface uses the `get\_axi\_ports` function of the \href{https://github.com/IObundle/py2hwsw/blob/main/py2hwsw/scripts/if_gen.py}{if\_gen.py} script.

% py2_macro: listing get_axi_ports from if_gen.py
% py2_macro: listing get_axi_read_ports from if_gen.py
% py2_macro: listing get_axi_write_ports from if_gen.py

The AXI interface extends configurable widths of the AXI Lite interface, with the following additions:
\begin{itemize}
  \item ID\_W
  \item SIZE\_W
  \item BURST\_W
  \item LOCK\_W
  \item CACHE\_W
  \item QOS\_W
  \item LEN\_W
\end{itemize}

The AXI interface supports the same 'params' as the AXI Lite interface.

For example, to add an AXI port to a core, add the following python dictionary to the core's ports list:
\begin{lstlisting}[language=python]
{
	"name": "example_port_m",
	"descr": "AXI manager port",
	"signals": {
		"type": "axil",
		"ADDR_W": 32,
		"DATA_W": 32,
		"PROT_W": 3,
		"RESP_W": 2,
		"ID_W": 4,
		"SIZE_W": 3,
		"BURST_W": 2,
		"LOCK_W": 2,
		"CACHE_W": 4,
		"QOS_W": 4,
		"LEN_W": 8,
	},
},
\end{lstlisting}


%
% APB
%
\clearpage
\large\textbf{APB}

The APB interface uses the `get\_apb\_ports` function of the \href{https://github.com/IObundle/py2hwsw/blob/main/py2hwsw/scripts/if_gen.py}{if\_gen.py} script.

% py2_macro: listing get_apb_ports from if_gen.py

The APB interface has the configurable widths:
\begin{itemize}
  \item ADDR\_W
  \item DATA\_W
\end{itemize}

For example, to add an APB port to a core, add the following python dictionary to the core's ports list:
\begin{lstlisting}[language=python]
{
	"name": "example_port_m",
	"descr": "APB manager port",
	"signals": {
		"type": "apb",
		"ADDR_W": 32,
		"DATA_W": 32,
	},
},
\end{lstlisting}


%
% AHB
%
\clearpage
\large\textbf{AHB}

The AHB interface uses the `get\_ahb\_ports` function of the \href{https://github.com/IObundle/py2hwsw/blob/main/py2hwsw/scripts/if_gen.py}{if\_gen.py} script.

% py2_macro: listing get_ahb_ports from if_gen.py

The AHB interface has the configurable widths:
\begin{itemize}
  \item ADDR\_W
  \item DATA\_W
  \item BURST\_W
  \item PROT\_W
  \item SIZE\_W
  \item TRANS\_W
\end{itemize}

For example, to add an AHB port to a core, add the following python dictionary to the core's ports list:
\begin{lstlisting}[language=python]
{
	"name": "example_port_m",
	"descr": "AHB manager port",
	"signals": {
		"type": "axil",
		"ADDR_W": 32,
		"DATA_W": 32,
		"BURST_W": 3,
		"PROT_W": 4,
		"SIZE_W": 3,
		"TRANS_W": 2,
	},
},
\end{lstlisting}


%
% Wishbone
%
\clearpage
\large\textbf{Wishbone}

The Wishbone interface uses the `get\_wb\_ports` function of the \href{https://github.com/IObundle/py2hwsw/blob/main/py2hwsw/scripts/if_gen.py}{if\_gen.py} script.

% py2_macro: listing get_wb_ports from if_gen.py

The Wishbone interface has the configurable widths:
\begin{itemize}
  \item ADDR\_W
  \item DATA\_W
\end{itemize}

For example, to add an Wishbone port to a core, add the following python dictionary to the core's ports list:
\begin{lstlisting}[language=python]
{
	"name": "example_port_m",
	"descr": "Wishbone manager port",
	"signals": {
		"type": "wb",
		"ADDR_W": 32,
		"DATA_W": 32,
	},
},
\end{lstlisting}


%
% IOb
%
\clearpage
\large\textbf{IOb Native}

The IOb Native interface is an open source interface developed by IObundle.
It simplifies the connections between core components due to its reduced amount of signals when compared to other standard interfaces.
The Py2HWSW core library~\ref{sec:core_lib} provides core's to convert between the IOb and other standard interfaces.
A description of the IOb interface is available at:
\url{https://github.com/IObundle/py2hwsw/blob/main/py2hwsw/lib/hardware/buses/iob_tasks/README.md}

The IOb interface uses the `get\_iob\_ports` function of the \href{https://github.com/IObundle/py2hwsw/blob/main/py2hwsw/scripts/if_gen.py}{if\_gen.py} script.

% py2_macro: listing get_iob_ports from if_gen.py

The IOb interface has the configurable widths:
\begin{itemize}
  \item ADDR\_W
  \item DATA\_W
\end{itemize}

For example, to add an IOb port to a core, add the following python dictionary to the core's ports list:
\begin{lstlisting}[language=python]
{
	"name": "example_port_m",
	"descr": "IOb manager port",
	"signals": {
		"type": "iob",
		"ADDR_W": 32,
		"DATA_W": 32,
	},
},
\end{lstlisting}


