% SPDX-FileCopyrightText: 2025 IObundle
%
% SPDX-License-Identifier: MIT

%
% Main classes
%

The \href{https://github.com/IObundle/py2hwsw/blob/main/py2hwsw/scripts/iob_conf.py}{iob\_conf} class is used to represent a configuration option of the core.
This class contains a set of attributes, each preceded by a comment describing the purpose of the attribute.

% Show iob_conf attributes
% py2_macro: class_attributes iob_conf from iob_conf.py
\href{https://github.com/IObundle/py2hwsw/blob/main/py2hwsw/scripts/iob_conf.py}{View Source}


The \href{https://github.com/IObundle/py2hwsw/blob/main/py2hwsw/scripts/iob_conf.py}{iob\_conf\_group} class is used to represent a group of configuration options.
This class contains a set of attributes, each preceded by a comment describing the purpose of the attribute.

% Show iob_conf_group attributes
% py2_macro: class_attributes iob_conf_group from iob_conf.py
\href{https://github.com/IObundle/py2hwsw/blob/main/py2hwsw/scripts/iob_conf.py}{View Source}

%
% Generator methods
%

The py2hwsw tool uses methods from the \href{https://github.com/IObundle/py2hwsw/blob/main/py2hwsw/scripts/config_gen.py}{config\_gen.py} script to generate the `*\_conf.vh` file, which contains all the Verilog macros that must be held for every design instance of the core.

Each generated Verilog macro is based on the attributes from the corresponding instance of the `iob\_conf` class.

% Show group generation of conf_vh
% py2_macro: listing conf_vh from config_gen.py
\href{https://github.com/IObundle/py2hwsw/blob/main/py2hwsw/scripts/config_gen.py}{View Source}


The py2hwsw tool uses methods from the \href{https://github.com/IObundle/py2hwsw/blob/main/py2hwsw/scripts/param_gen.py}{param\_gen.py} script to generate the Verilog parameters code that is automatically inserted in the core's Verilog module and instances.

Each generated Verilog parameter is based on the attributes from the corresponding instance of the `iob\_conf` class.

% Show verilog param generation
% py2_macro: listing generate_params from param_gen.py
\href{https://github.com/IObundle/py2hwsw/blob/main/py2hwsw/scripts/param_gen.py}{View Source}
