% SPDX-FileCopyrightText: 2025 IObundle
%
% SPDX-License-Identifier: MIT

The setup directory of a core may have the following structure:

\begin{verbatim}
.
├── core_name.py
├── core_name.json
├── document
│   ├── doc_build.mk
│   ├── figures
│   └── tsrc
├── hardware
│   ├── src
│   ├── fpga
│   │   ├── fpga_build.mk
│   │   ├── src
│   │   ├── quartus
│   │   └── vivado
│   ├── modules
│   ├── simulation
│   │   ├── sim_build.mk
│   │   └── src
│   └── syn
│       ├── src
│       └── genus
├── software
│   ├── sw_build.mk
│   └── src
├── scripts
├── submodules
├── Makefile
├── README.md
├── LICENSE
├── CITATION.cff
└── default.nix
\end{verbatim}

Only the \texttt{core\_name.py} or \texttt{core\_name.json} file is needed to
pass the core's description to Py2HWSW.  The remaining directories and files are
optional.

If the \texttt{document}, \texttt{hardware}, and \texttt{software} directories
exist, they will be copied to the \texttt{build} directory, overriding any files
already present there, such as standard ones or files from other cores.

The \texttt{*\_build.mk} files allow the user to include core specific Makefile
targets and variables from the build process.  These will be copied to the
\texttt{build} directory and included in the standard build process Makefiles.

The \texttt{src} directories contain manually written Verilog/C/TeX sources for
the core, should they be needed.

The following directories and files do not follow a mandatory structure, but are
typically used for the following purposes:

The \texttt{hardware/modules} and \texttt{submodules} directories typically
contain setup directories of other cores.

The \texttt{scripts} directory contains scripts specific to the core, and may be
called by the user or from the \texttt{core\_name.py} script.

A simple example of a core's setup directory is available for the
\href{https://github.com/IObundle/py2hwsw/tree/main/py2hwsw/lib/hardware/basic_tests/iob_and}{iob\_and}
core.

A more complex example of a core's setup directory is available for the
\href{https://github.com/IObundle/iob-soc}{iob\_soc} core.
