% SPDX-FileCopyrightText: 2025 IObundle
%
% SPDX-License-Identifier: MIT

Py2HWSW supports a \textit{Universal Test Bench}.

To use the \textit{Universal Test Bench}, the core needs to provide the following files:
\begin{itemize}
  \item iob\_v\_tb.vh
  \item iob\_uut.v
  \item iob\_core\_tb.c
  \item sw\_build.mk
\end{itemize}


Create the \textbf{iob\_v\_tb.vh} testbench header source and define the \textbf{IOB\_CSRS\_ADDR\_W} macro to specify the address width of the simulation wrapper's CSRs bus (the width must be large enough address all CSRs from all verification instruments).
For example, the iob\_uart core's simulation wrapper only uses one verification instrument (the iob\_uart core itself). Therefore, the testbench should define the \textbf{IOB\_CSRS\_ADDR\_W} macro to have the same width as the iob\_uart core's CSRs bus.
The iob\_uart core's CSRs header files are also included because we can obtain the CSRs bus width from the auto-generated macro \textit{IOB\_UART\_CSRS\_ADDR\_W}
% py2_macro: file iob_uart/hardware/simulation/src/iob_v_tb.vh


Create \textbf{iob\_uut.v} simulation wrapper and instantiate the verification instruments.
For example, the iob\_uart core is also used as a verification instrument to test itself. It is instantiated in the uart's iob\_uut.v file, and its RS232 ports are connected in loopback. The iob\_uut.v file is generated from the iob\_uart\_sim.py core's attributes (using the Py2HWSW attribute: "name": "uut").
% py2_macro: file iob_uart_sim.py


Create the \textbf{iob\_core\_tb.c} source to drive the verification instruments (instantiated in the simulation wrapper).
For example, the iob\_uart core's testbench drives this core, writing data to it, and reading back the data received from the loopback.
% py2_macro: file iob_uart/software/src/iob_core_tb.c

Create the \textbf{sw\_build.mk} makefile segment and add the `tb` target to the `UTARGETS` list. Adding this target will cause the testbench software to be built. This testbench software will run on the host machine in parallel to the simulation.
Also add the verification instrument's CSRs sources to the `CSRS` list.
Also update the `TB\_INCLUDES` list as needed.
% py2_macro: file iob_uart/software/sw_build.mk
