% SPDX-FileCopyrightText: 2025 IObundle
%
% SPDX-License-Identifier: MIT

Py2HWSW allows users to customize its behavior and core generation process. When running cores directly from the cloned Py2HWSW repository, users can modify the cores or Py2HWSW scripts for debugging purposes.

The Py2HWSW repository contains several main folders, including lib, scripts, and generic folders.
\begin{verbatim}
.
└── py2hwsw
     ├── <py2 generic folders>
     ├── lib
     └── scripts
\end{verbatim}

The py2hwsw folder contains generic folders that are copied to every core build directory set up via Py2HWSW. These folders include standard Makefiles, FPGA board constraints, simulator dependencies, and other essential files.

To override the default files, users can create a file with the same name in their core's setup directory. For example, to override the default py2hwsw/document/tsrc/sim\_desc.tex, create a new document/tsrc/sim\_desc.tex in the core's setup directory. Py2HWSW will first copy the generic default file to the build directory and then copy the core files from the setup directory, overriding the default file.

The lib directory contains a library of cores provided by Py2HWSW. These cores are intended to be bug-free and do not typically require modifications. However, if users need to modify a core for their project, they can copy the corresponding core's setup directory to a subfolder in their project directory. Py2HWSW will use the first core it finds with the required name, so users can create custom modifications to the core specific to their project.

For example, to modify the iob\_and core, copy its folder from the Py2HWSW repository and place it in the user's project directory. When calling Py2HWSW from the project directory, it will find the copied iob\_and folder first and use it to generate the iob\_and core.

The scripts folder contains the Python scripts that make up the Py2HWSW tool. These scripts are typically only modified by developers, as they directly change the Py2HWSW program's behavior. However, users can modify these scripts for quick bug fixes or to add custom functionality.

By customizing Py2HWSW, users can tailor the tool to their specific needs and create custom cores and workflows. This flexibility allows users to adapt Py2HWSW to their project's requirements and create complex digital designs with ease.
